---
output:
  html_document: default
  word_document: default
---
MY first R Markdown file
============================

This is my first R markdown file.

Here, we're going to load some data.

```{r}
library(datasets)
data(airquality)
summary(airquality)
```

Let's first make a paris plot of the data

```{r}
pairs(airquality)
```

Here's a regression model of ozone on wind, solar radiation, and temperature.

```{r}
library(stats)
fit <- lm(Ozone ~Wind + Solar.R + Temp, data = airquality)
summary(fit)
```


Here's an unordered list:

* First element

* Second element


Let's first simulate some data.
```{r simulatedata, echo = TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```
Here is a scatterplot of the data.
```{r scatterplot, fig.height = 4}
par(mar=c(5,4,1,1), las = 1)
plot(x,y,main = "My simulated Data")
```


## Introduction

```{r fitmodel}
library(datasets)
data("airquality")
fit <- lm(Ozone ~Wind + Solar.R + Temp, data = airquality)
```
Here is a table of regression coefficients.
```{r showtable, results="asis"}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type="html")
```


Sometimes we want to set options for every code chunk that

```{r setoptions, echo = FALSE}
opts_chunk$set(echo = FALSE, results = "hide")
```
First simulate data
```{r simulatedata, echo=TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = 0.5)
```
Here is a scatterplot of the data.
```{r scatterplot, fig.height=4}
par(mar = c(5,4,1,1), las = 1)
plot(x,y,main = "My Simulated Data")
```
